---
title: 'Assigment #2'
author: "Yiming Jin"
date: "10/10/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(mapview)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot)
library(jtools)     # for regression model plots

# functions
mapTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 14,colour = "black"),
    plot.subtitle=element_text(face="italic"),
    plot.caption=element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2)
  )
}

plotTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 14,colour = "black"),
    plot.subtitle = element_text(face="italic"),
    plot.caption = element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_line("grey80", size = 0.1),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2),
    strip.background = element_rect(fill = "grey80", color = "white"),
    strip.text = element_text(size=12),
    axis.title = element_text(size=12),
    axis.text = element_text(size=10),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"),
    strip.text.x = element_text(size = 14)
  )
}

palette5 <- c("#25CB10", "#5AB60C", "#8FA108",   "#C48C04", "#FA7800")

qBr <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(quantile(round(df[[variable]],0),
                          c(.01,.2,.4,.6,.8), na.rm=T))
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]]), digits = 3),
                          c(.01,.2,.4,.6,.8), na.rm=T)
  }
}

q5 <- function(variable) {as.factor(ntile(variable, 5))}

nn_function <- function(measureFrom,measureTo,k) {
  measureFrom_Matrix <- as.matrix(measureFrom)
  measureTo_Matrix <- as.matrix(measureTo)
  nn <-   
    get.knnx(measureTo, measureFrom, k)$nn.dist
    output <-
      as.data.frame(nn) %>%
      rownames_to_column(var = "thisPoint") %>%
      gather(points, point_distance, V1:ncol(.)) %>%
      arrange(as.numeric(thisPoint)) %>%
      group_by(thisPoint) %>%
      summarize(pointDistance = mean(point_distance)) %>%
      arrange(as.numeric(thisPoint)) %>% 
      dplyr::select(-thisPoint) %>%
      pull()
  
  return(output)  
}
```

## Data Wrangling

```{r setup, include=FALSE}
### dat <- st_read("/Users/yimingjin/Desktop/MUSA_508/4th&5th. Lec + Lab/Lab4-5/studentsData.geojson")
### mapview::mapview(dat)
### Sorry but I have to used the link on my laptop here. 

dat <- st_read("E:/Fall2020/MUSA-508_PublicPolicyAnalytics/Mid_term_Project/studentsData.geojson")
mapview::mapview(dat)

miami.base <- 
  st_read("https://opendata.arcgis.com/datasets/5ece0745e24b4617a49f2e098df8117f_0.geojson")%>%
  filter(NAME %in% c("MIAMI","MIAMI BEACH")) 

dat <- dat%>%
  mutate(priceFt=SalePrice/LivingSqFt)

ggplot()+
  geom_sf(data=st_union(miami.base), fill = "grey40",alpha=0.5)+
  geom_sf(data = st_centroid(dat), aes(colour=q5(priceFt)),size=0.5)+
  scale_colour_manual(values = palette5,
                      labels = qBr(dat, "priceFt"),
                      name = "Price/ft^2")+
  labs(title = "Price per square foot")+
  mapTheme()

```
## Facotrs for public servives
```{r}

### landmark (facilities such as parks, schools, parking lots, restaurant, etc.) 
### https://datahub-miamigis.opendata.arcgis.com/datasets/landmarks/data?page=10
landsmark <- st_read("hhttps://opendata.arcgis.com/datasets/d74e47be08ff41f9ae88beba2064203c_0.geojson")

### parks 
### https://gis-mdc.opendata.arcgis.com/datasets/park-facility/geoservice?geometry=-80.463%2C25.688%2C-79.942%2C25.797
park <- st_read("https://opendata.arcgis.com/datasets/8c9528d3e1824db3b14ed53188a46291_0.geojson")

### Transit station
### https://gis-mdc.opendata.arcgis.com/datasets/metrorail-station/geoservice
metrorail <- st_read("https://opendata.arcgis.com/datasets/ee3e2c45427e4c85b751d8ad57dd7b16_0.geojson")
```

## Facotrs for internal characteristics

```{r}
names(dat)
### Then use "dat <- dplyr::select()" to select the internal characteristics
```

## Separate train data
```{r}
dat_toPredict <- subset(dat, dat$SalePrice == 0)
dat_toTrain <- subset(dat, dat$SalePrice != 0)
```

## Correlation
```{r}
### Corr matrix
numericVars <- 
  select_if(st_drop_geometry(dat_toPredict), is.numeric) %>% na.omit()

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables") 
```
## Multivariate Linear Regression
```{r}
### reg1 <- lm(SalePrice ~ ., data = st_drop_geometry(boston.sf) %>% 
###                                 dplyr::select(SalePrice, LivingArea, 
###                                               GROSS_AREA, R_TOTAL_RM, NUM_FLOORS,
###                                               R_BDRMS, R_FULL_BTH, R_HALF_BTH, 
###                                              R_KITCH, R_FPLACE))
### summary(reg1)
```


## Measure generalizability __ Cross-validation
```{r}
### use caret package cross-validation method
### k = 10, may need to be changed later
fitControl <- caret::trainControl(method = "cv", 
                           number = 10,
                           # savePredictions differs from book
                           savePredictions = TRUE)
set.seed(717)
### crimes.buffer feature added
### for k-folds CV
reg.cv <- 
  caret::train(SalePrice ~ ., data = st_drop_geometry(dat_toTrain) %>% 
                                dplyr::select(SalePrice, LotSize,  
                                               Bed, YearBuilt), 
     method = "lm", 
     trControl = fitControl, 
     na.action = na.pass)

reg.cv
### Need to select the variables later in the dplyr:select 

### visualize the k-folds results

reg.cv$resample

reg.cv$resample %>% 
  pivot_longer(-Resample) %>% 
  mutate(name = as.factor(name)) %>% 
  ggplot(., aes(x = name, y = value, color = name)) +
  geom_jitter(width = 0.1) +
  facet_wrap(~name, ncol = 3, scales = "free") +
  theme_bw() +
  theme(
    legend.position = "none"
  )

```
## Interpret the spread of values between the folds

```{r}
# extract predictions from CV object
cv_preds <- reg.cv$pred
# compare number of observations between data sets (why we have to do so?)
nrow(dat_toTrain)
nrow(cv_preds)

## Create dataset with "out of fold" predictions and original data

map_preds <- dat_toTrain %>% 
  rowid_to_column(var = "rowIndex") %>% 
  left_join(cv_preds, by = "rowIndex") %>% 
  mutate(SalePrice.AbsError = abs(pred - SalePrice)) %>% 
  cbind(st_coordinates(.))

### !!!It is strange to show that the numbers of rows are different since in this step since the nrow()shows that the dat_toTrain and cv_predict ARE THE SAME IN COLUMN NUMBER!!!

# weird CRS fix to dat_toTrain
#st_crs(map_preds) <- st_crs(nhoods)

### Need we find a neighborhood map ourselves with geo info??

### plot errors on a map
#ggplot() +
#    geom_sf(data = nhoods, fill = "grey40") +
#    geom_sf(data = map_preds, aes(colour = q5(SalePrice.AbsError)),
#            show.legend = "point", size = 1) +
#    scale_colour_manual(values = palette5,
#                     labels=qBr(map_preds,"SalePrice.AbsError"),
#                     name="Quintile\nBreaks") +
#    labs(title="Absolute sale price errors on the OOF set",
#        subtitle = "OOF = 'Out Of Fold'") +
#    mapTheme()
```


## Spatial Correlation of Error

```{r}

#inTrain <- createDataPartition(
#              y = paste(dat_toTrain$$Name, dat_toTrain$NUM_FLOORS.cat, 
#                        dat_toTrain$Style, dat_toTrain$R_AC), 
#              p = .60, list = FALSE)
#miami.training <- dat_toTrain[inTrain,] 
#miami.test <- dat_toTrain[-inTrain,]  

### How to create "Name" column in the dat_toTrain? Does the name of Boston.sf data come from the neighborhood map?

```

```{r}
reg.training <- 
  lm(SalePrice ~ ., data = as.data.frame(miami.training) %>% 
                             dplyr::select(SalePrice, LivingArea, Style, 
                                           GROSS_AREA, NUM_FLOORS.cat,
                                           R_BDRMS, R_FULL_BTH, R_HALF_BTH, 
                                           R_KITCH, R_AC, R_FPLACE, crimes.Buffer))

miami.test <- 
  miami.test %>%
  mutate(Regression = "Baseline Regression",
         SalePrice.Predict = predict(reg.training, boston.test),
         SalePrice.Error = SalePrice.Predict - SalePrice,
         SalePrice.AbsError = abs(SalePrice.Predict - SalePrice),
         SalePrice.APE = (abs(SalePrice.Predict - SalePrice)) / SalePrice.Predict)%>%
  filter(SalePrice < 5000000) 
```

## Examine if there exist Spatial Correlation of Errors
```{r}
### knn + Moran's I 
```

## Neighborhood Fixed Effect

```{r}
reg.nhood <- lm(SalePrice ~ ., data = as.data.frame(miami.training) %>% 
                                 dplyr::select(Name, SalePrice, LivingArea, 
                                               Style, GROSS_AREA, NUM_FLOORS.cat,
                                               R_BDRMS, R_FULL_BTH, R_HALF_BTH, 
                                               R_KITCH, R_AC, R_FPLACE,crimes.Buffer))

miami.test.nhood <-
  miami.test %>%
  mutate(Regression = "Neighborhood Effects",
         SalePrice.Predict = predict(reg.nhood, miami.test),
         SalePrice.Error = SalePrice - SalePrice.Predict,
         SalePrice.AbsError = abs(SalePrice - SalePrice.Predict),
         SalePrice.APE = (abs(SalePrice - SalePrice.Predict)) / SalePrice) %>%
  filter(SalePrice < 5000000)
```

## Answer for the final results

```{r}
# model coefficents for each Neighborhood
tidy(reg.nhood) %>% 
  filter(str_detect(term, "Name")) %>% 
  kable() %>% 
  kable_styling()
```
